\Title

### 2016-08-18 manuscript/manuscript.tex
Explain amazon and parana basin discrepancies

In general, our model fits both the seismological and gravity data well
in the oceans and in the Atlantic coast.
The Parnaíba Basin has deep Moho surrounding its continental borders, following
inward with a shallower Moho, then a deeper step, and finally a shallower
part in the middle of the basin.
Our model has small differences with the few seismological data points that
fall inside and on the borders of the basin.
However, recent deep seismic reflection studies by \citet{daly2014} that cross
the basin in from west to east agree with our model.
Our model reveals a deep Moho in the Northern border of the Parecis Basin that
is corroborated by a single seismological data point.

>>>>

In the Amazon and Paraná Basins, our model underestimates the seismological
data by up to 15 km but fits the gravity data.
This indicates that a mass excess is present in the crust or upper mantle.
A body with positive density contrast that was unaccounted in the data
processing will make the observed gravity disturbance greater than it would
be otherwise.
This will lead the inversion to produce a shallower Moho estimate.
These discrepancies between gravity and seismological estimates has been noted
before by \citet{nunn1988} for the Amazon Basin and \citet{mariani2013}
for the Paraná Basin.
Both studies propose high density rocks in the lower crust as probable causes
for the discrepancies.
Another possible cause for the observed discrepancy in our model is our failure
to fully remove from the data the igneous intrusions present in both basins.
Our sediment correction was performed with the CRUST1.0 model
\citep{laske2013}.
Using a more detailed sediment model for South America might lead to more
accurate results for these basins.

Greater confidence in our Moho model can be had in areas where it is able to
fit both the gravity and the seismological data.
In such places, a gravity-derived model can serve as a better interpolator for
the seismological point estimates.
In general, our model fits both both data sets in the oceans and in the
Atlantic coast of the continent.
The Parnaíba Basin has deep Moho surrounding its continental borders, following
inward with a shallower Moho, then a deeper step, and finally a shallower
part in the middle of the basin.
Our model has small differences with the few seismological data points that
fall inside and on the borders of the basin.
However, recent deep seismic reflection studies by \citet{daly2014} that cross
the basin in from west to east agree with our model.
Our model reveals a deep Moho in the Northern border of the Parecis Basin that
is corroborated by a single seismological data point.
